What can GitHub and Googlecode Issues tell us about Exceptions in Android?

### 2014-08-29 android-stacks.tex
more fine grained in sec 2

Android is an open source platform for mobile devices based on Linux kernel,
which also contains  a core Java library, a set of libraries third-party libraries (e.g.  SQLite),
the Dalvik runtime environment, and the Application Framework (which provides higher-level services to the applications
running on the platform).

The Android Application Framework supports an event-driven development model. 
Among the basic elements that comprise an Android application, we can cite the
Activity. Each application usually defines one Activity per application Window.
 Each Activity defines a set of hook methods  (e.g., OnCreate(), onPause()) that are dispatched
automatically by the Android framework (by inversion of
control [ref]), in response to infrastructure and application events.

Due to the high demand for responsiveness in mobile environment (mobile apps can easily become 
unresponsivedue due to resurce limitation and excessive network access [shimidit and arie]) the
Android Application Framework also provides APIs to support concurrent developement (e.g. AsyncTask).

Android platform is mostly implemented in Java, uses JNI[ref] to access native C code, and 
reuses the embedded Java Exception model to detect and handle abnormal computation states.

>>>>

Android is an open source platform for mobile devices based on Linux kernel,
which also contains  a core Java library, a set of libraries third-party libraries (e.g.  SQLite),
the Dalvik runtime environment, and the Application Framework (which provides 
higher-level services to the applications running on the platform) ~cite{andguide}.
Android platform is mostly implemented in Java and uses JNI[ref] to access native C/C++ code. 
And as mentioned before, it reuses the embedded Java Exception model to detect and handle 
abnormal computation states.

The Android Application Framework supports an event-driven development model. 
Among the basic elements that comprise an Android application, we can cite the
Activity. Each application usually defines one Activity per application Window.
 Each Activity defines a set of hook methods  (e.g., OnCreate(), onPause()) that are dispatched
automatically by the Android framework (by inversion of
control), in response to infrastructure and application events.

Due to the high demand for responsiveness in mobile environment (mobile apps can easily become 
unresponsivedue due to resurce limitation and excessive network access) the
Android Application Framework also provides APIs to support concurrent 
developement (e.g. AsyncTask).
